### 2022-10-24 manuscript.Rmd
Change folder structure for saving data

```{r}
intermediate_results <- here("intermediate_results/")
if(fs::dir_exists(intermediate_results))
 fs::dir_delete(intermediate_results)
unzip("intermediate_results_separability.zip", junkpaths = TRUE)
unzip(here("intermediate_results_reliability.zip"), junkpaths = TRUE)
unzip(here("intermediate_results_type1error_1.zip"), junkpaths = TRUE)
unzip(here("intermediate_results_type1error_2.zip"), junkpaths = TRUE)
unzip(here("intermediate_results_type1error_3.zip"), junkpaths = TRUE)
```

@@

results_load_model3 <- 
  read.csv(here::here("results_load_model3.csv"))
results_cov_model3 <- 
  read.csv(here::here("results_cov_model3.csv"))

@@

results_load_model1 <-
  read.csv(here::here("results_load_model1.csv"))
results_load_model2 <-
  read.csv(here::here("results_load_model2.csv"))
results_cov_model2  <-
  read.csv(here::here("results_cov_model2.csv"))
results_load_model3 <-
  read.csv(here::here("results_load_model3.csv"))
results_cov_model3  <- 
  read.csv(here::here("results_cov_model3.csv"))

>>>>

```{r}
intermediate_results <- here("intermediate_results/")
if(fs::dir_exists(intermediate_results))
 fs::dir_delete(intermediate_results)
unzip(here("data", "intermediate_results_separability.zip"), junkpaths = TRUE, exdir =here("data"))
unzip(here("data", "intermediate_results_reliability.zip"), junkpaths = TRUE, exdir =here("data"))
unzip(here("data", "intermediate_results_type1error_1.zip"), junkpaths = TRUE, exdir =here("data"))
unzip(here("data", "intermediate_results_type1error_2.zip"), junkpaths = TRUE, exdir =here("data"))
unzip(here("data", "intermediate_results_type1error_3.zip"), junkpaths = TRUE, exdir =here("data"))
```

@@

results_load_model3 <- 
  read.csv(here::here("data", "results_load_model3.csv"))
results_cov_model3 <- 
  read.csv(here::here("data", "results_cov_model3.csv"))

@@

results_load_model1 <-
  read.csv(here::here("data", "results_load_model1.csv"))
results_load_model2 <-
  read.csv(here::here("data", "results_load_model2.csv"))
results_cov_model2  <-
  read.csv(here::here("data", "results_cov_model2.csv"))
results_load_model3 <-
  read.csv(here::here("data", "results_load_model3.csv"))
results_cov_model3  <- 
  read.csv(here::here("data", "results_cov_model3.csv"))
